Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-04 paper/Intuition.tex
intuition

\section{Intuition}
\label{Sec:ProofStructure}

In this section, we present the proof structure for our MSI-based cache
coherence protocol of Figure \ref{trans}. Specifically, we formally reduce the
proof of the store atomicity theorem for the whole system to the proof of a set
of invariants. In order to prove these invariants we introduce the main
``intuition'' behind the correctness of the protocol. This intuition is not
restricted to the MSI-based protocol; Section \ref{Sec:Refinements} shows that
it applies to other protocols like MOSI.

>>>>

\section{Proof of MSI protocol being sound wrt Store atomicity}
\label{safety}

In this section, we present the proof structure for the soundness property of our
MSI-based cache coherence protocol of Figure \ref{trans}. Specifically, we
formally reduce the proof of the store atomicity theorem for the whole system
to the proof of a set of invariants. In order to prove these invariants we
introduce the main ``intuition'' behind the correctness of the protocol. This
intuition is not restricted to the MSI-based protocol; Section
\ref{Sec:Refinements} shows that it applies to other protocols like MOSI.
